% !TEX TS-program = pdflatex
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{kotex}
\usepackage{hyperref}
\usepackage{fancyhdr}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\setlength{\headheight}{26pt}
\setlist[itemize]{leftmargin=1.5em, itemsep=0.3em, topsep=0.1em}
\titleformat{\section}{\Large\scshape}{}{0pt}{}[\vspace{0.3em}\titlerule]
\titlespacing*{\section}{0pt}{1.6em}{0.9em}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\itshape Seth Han --- Curriculum Vitae \\ Updated on: 12/04/2025}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\begin{center}
\textbf{\Large Seth Han} \\
School of Arts \& Sciences, Dartmouth College, Hanover, NH, USA \\
Phone: +1 (603) 276-5846 \textbar \; Email: \href{mailto:seth.s.han.29@dartmouth.edu}{seth.s.han.29@dartmouth.edu} \\
LinkedIn: \href{https://www.linkedin.com/in/seth-han/}{linkedin.com/in/seth-han}
\end{center}

\section*{\textbf{Education}}
\textbf{Dartmouth College}, Hanover, NH, USA \hfill 2025 -- 2029 \\
Bachelor of Arts in Engineering Sciences and Music (GPA: 4.0/4.0)

\textbf{Cheongshim International Academy}, Gyeonggi, South Korea \hfill 2022 -- 2025 \\
High School Diploma (GPA: 5.0/5.0 Unweighted)

\section*{\textbf{Research Experience}}
\begin{itemize}
    \item \textbf{Undergraduate Researcher}, CREATE Lab at Dartmouth College \hfill 2026 --
    \\Machine learning for robust state estimation of virtual power plant under cyber attacks
    \\(Advisors: Prof. Junbo Zhao\textsuperscript{\textdagger\ \textpilcrow}, Dr. Alaa Selim\textsuperscript{\textdagger} \& Mr. Yingrui Fan\textsuperscript{\textdagger})

    \item \textbf{Independent Researcher}, School of Arts \& Sciences at Dartmouth College \hfill 2025 --
    \\Topology-aware weakly-supervised semantic segmentation (WSSS) for anomaly detection for manufacturing
    \\(Co-fisrt author: Mr. Seungjun Chu\textsuperscript{\textdaggerdbl})

    \item \textbf{Research Scientist}, Drice \hfill 2022 -- 2025
    \\Drone-based black ice detection and mapping using YOLOX
    \\(Advisors: Dr. Hyunwook Chung\textsuperscript{\textsection} \& Mr. Donghwan Shin\textsuperscript{\textsection})

    \item \textbf{Student Researcher}, Cheongshim International Academy \hfill 2024 -- 2025
    \\Gait-recognition based missing person identification from CCTV footage
    \\(Advisor: Mr. Donghwan Shin\textsuperscript{\textsection})
    
    \item \textbf{Student Researcher}, Cheongshim International Academy \hfill 2021 -- 2022
    \\Heavy metal absorption using used mushroom compost
    \\(Advisor: Dr. Hyunchang Hong\textsuperscript{*})\\

    \textsuperscript{\textdagger}Thayer School of Engineering, Dartmouth College, Hanover, NH\\
    \textsuperscript{\textpilcrow}DOE Northeast University Cybersecurity Center for Advanced and Resilient Energy Delivery, Storrs, CT\\
    \textsuperscript{\textdaggerdbl}College of Engineering, Korea University, Seoul, South Korea\\
    \textsuperscript{\textsection}Department of Mathematics, Cheongshim International Academy, Gyeonggi, South Korea\\
    \textsuperscript{*}Department of Science, Cheongshim International Academy, Gyeonggi, South Korea
\end{itemize}

\section*{\textbf{Professional Experience}}
\begin{itemize}
    \item \textbf{Co-Founder \& CIO}, Drice \hfill 2022 -- 2025
    \\Developed and patented an AI-powered drone system that detects black ice in real-time. Secured \$11K+ in R\&D funding from the Ministry of Science of Korea, Ministry of Education of Korea, POSCO DX, etc.

    \item \textbf{Data Analyst Intern (CTO Staff)}, Enuma, Inc. \hfill 2025 -- 2025
    \\Analyzed user log from B2G edtech products in global markets using SQL and Python.
    
    \item \textbf{Co-Founder \& CSO}, Justiz \hfill 2023 -- 2024
    \\Built a language analysis platform to detect malicious comments and help influencers pursue legal action or data-driven business decisions. Secured \$11K+ in R\&D funding from the Ministry of Science of Korea.

    \item \textbf{Research Assistant Intern (CEO Staff)}, Enuma, Inc.\hfill 2024 -- 2024
    \\Researched edtech industry trends to enhance educational games for slow learners, presenting findings biweekly to the CEO and the CPO. Assisted in developing government-certified digital English and Mathematics textbooks in South Korea.
\end{itemize}

\section*{\textbf{Journal Papers}}
\begin{itemize}
    \item J. OH\textsuperscript{\textdagger}, J. Moon\textsuperscript{\textdagger}, \underline{S. HAN\textsuperscript{\textdagger}}, and D. SHIN, “Real-Time Black Ice Detection in Drone View Using YOLOX”, \textit{J Stud Res}, vol. 13, no. 2, May 2024. DOI: 10.47611/jsrhs.v13i2.6831\\%
    (\textsuperscript{\textdagger}Co-first authors)
\end{itemize}

\section*{\textbf{Patents}}
\begin{itemize}
    \item J. Oh, H. Lee, S. Moon, and \underline{S. Han}, "Black Ice Identification and Warning System and Method Using Unmanned Aerial Vehicles," KR Patent 10-2681032, Jul. 04, 2024.
\end{itemize}

\section*{\textbf{Selected Scholarships \& Awards}}

\textbf{\textit{Scholarships}}
\begin{itemize}
    \item Presidential Science Scholarship of South Korea \hfill 2025 -- 2029 \\(merit-based \$50,000/year scholarship for 20 students nationwide)
    \item James and Agnes Kim Family Scholarship \hfill 2025 -- 2026 \\(Dartmouth Honorary Paired Scholarship)\\
\end{itemize}

\textbf{\textit{Awards}}
\begin{itemize}
    \item Finalist \& National Rep., Regeneron International Science \& Engineering Fair (ISEF) \hfill 2024
    \item Minister of Science Award \& Provincial Rep., National Science Contest in Engineering \hfill 2024
    \item Deputy Prime Minister/Minister of Education Award, STEAM R\&E in Engineering \hfill 2024
    \item 1st Place, Korea Science \& Engineering Fair (KSEF) in Computer Science \hfill 2024
    \item 3rd Place, POSCO DX AI Youth Challenge \hfill 2024
    \item 1st Place, Gyeonggi Science Contest in Engineering \hfill 2024
    \item School Merit Award: Experiment \& Research \hfill 2024
    \item School Merit Award: Giftedness in Science \hfill 2024
    \item 2nd Place, Korea Science \& Engineering Fair (KSEF) in Computer Science \hfill 2023
    \item 1st Place \& National Rep., Youth International Science Fair (YISF) in Env. Sci. \hfill 2022
    \item Deputy Prime Minister/Minister of Education Award, STEAM R\&E in Engineering \hfill 2022
    \item 2nd Place, Korea Science \& Engineering Fair (KSEF) in Env. Sci. \hfill 2022
    \item 2nd Place \& Provincial Rep., Korea Youth Startup Competition \hfill 2022
    \item Finalist \& Innovation Award, Promising Student Start-up Team 300+ \hfill 2022
    \item School Merit Award: Giftedness in Science \hfill 2022
    \item 2nd Place, Youth Science Club (YSC) in Env. Sci. \hfill 2021
\end{itemize}

\section*{\textbf{Selected Activities and Engagements}}
\begin{itemize}
    \item \textbf{Executive Board Member}, DartUP Dartmouth \hfill 2025 --\\
    Organized Dartmouth’s Social Blueprint Challenge (SBC, Hult Prize campus round). Designed and led a social entrepreneurship curriculum for SBC participants \& 30+ associate members.

    \item \textbf{Magnuson First Year Fellow}, Magnuson Center for Entrepreneurship \hfill 2025 --\\
    Selected as 1 of 15 for entrepreneurship and leadership training. Mentored by the Magnuson Student Leadership Board and Entrepreneurial Thinking \& Leadership Fellows.

    \item \textbf{Great Issues Scholar in Residence}, Dickey Center for Int'l Understanding \hfill 2025 --\\
    Participated in a year-long series of interactive events around topics like global health, climate change, gender in politics, international development, and regional security challenges.

    \item \textbf{Film Producer \& Editor}, Independent \hfill 2019 -- 2025\\
    Participated in 10+ individual film and commercial video projects. Most recent work \textit{Yellow Ghost} made it onto the selection list of the Busan International Film Festival (BIFF) 2025.
\end{itemize}

\end{document}
